\vspace{1.0cm} \Large \bf Supplemental material of ``Health and disease imprinted in the time variability of the human microbiome''

### 2017-01-13 mSystems/rev/mSys_suppl_rev.tex
Corrections and pre-submission, which leads to REVISION draft I
Changes to be committed:
	modified:   figs/supfig_taxlev1.eps
	modified:   figs/supfig_taxlev2.eps
	modified:   mSys_MAIN_rev.pdf
	modified:   mSys_MAIN_rev.tex
	modified:   mSys_MAIN_rev_marked.docx
	modified:   mSys_MandM_rev.tex
	modified:   mSys_discussion_rev.tex
	modified:   mSys_suppl_rev.pdf
	modified:   mSys_suppl_rev.tex
	new file:   tab/mSys_suppl_tab1.pdf
	new file:   tab/mSys_suppl_tab2.pdf
	new file:   tab/mSys_suppl_tab3.pdf
	new file:   tab/mSys_suppl_tab4.pdf
	new file:   tab/mSys_suppl_tab5.pdf
	new file:   tab/m

% watermarks (time consuming!)
\newwatermark[allpages,color=Mulberry!4,angle=45,scale=7,xpos=-40,ypos=0]{REVISION}
\newwatermark[allpages,color=Mulberry!12,angle=0,scale=1,xpos=0,ypos=137]{
\emph{mSystems} \LaTeX\ manuscript \releasecode}

@@

% line numbering
\usepackage[running,mathlines]{lineno}
\renewcommand\thelinenumber{\color{red}\arabic{linenumber}}
\linenumbers

% bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,font=small]{caption}
\captionsetup[table]{name=Supplementary Table S\!\!}

@@

% Disable page numbering
%\pagenumbering{gobble}

\title{
	\vspace*{0mm} % May help to include the corresponding author footnote in the title page
	\singlespacing
	\begin{flushleft}
		\texttt{\large Title:} \\
	\end{flushleft}
	\vspace*{2mm}
	Supplemental material of "Health and disease imprinted in the time variability of the human microbiome"\\
	\vspace*{6mm}
	\begin{flushleft}
		\texttt{\large Running title:} \\
	\end{flushleft}
	\vspace*{0mm}
	Supplemental material of "Microbiota, are you sick?"
	\vspace*{4mm}
	}

@@

>>>>

% watermarks (time consuming!)
%\newwatermark[allpages,color=Mulberry!4,angle=45,scale=7,xpos=-40,ypos=0]{REVISION}
%\newwatermark[allpages,color=Mulberry!12,angle=0,scale=1,xpos=0,ypos=137]{
%\emph{mSystems} \LaTeX\ manuscript \releasecode}

@@

% line numbering
\usepackage[running,mathlines]{lineno}
\renewcommand\thelinenumber{\color{red}\arabic{linenumber}}
%\linenumbers

% bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,font=small]{caption}
\captionsetup[table]{name=Supplementary Table S\!\!}
%\DeclareCaptionFormat{empty}{}  %%%%% COMMENT THIS LINE AND THE NEXT FOR REACTIVATING CAPTIONS %%%%%
%\captionsetup{format=empty,aboveskip=0pt,belowskip=0pt} %%%%%

@@

% Disable page numbering
\pagenumbering{gobble}

\title{
	\vspace*{0mm} % May help to include the corresponding author footnote in the title page
	\singlespacing
	\begin{flushleft}
		\texttt{\large Title:} \\
	\end{flushleft}
	\vspace*{2mm}
	Supplementary tables of "Health and disease imprinted in the time variability of the human microbiome"\\
	\vspace*{6mm}
	\begin{flushleft}
		\texttt{\large Running title:} \\
	\end{flushleft}
	\vspace*{0mm}
	Supplementary tables of "Microbiota, are you sick?"
	\vspace*{4mm}
	}

@@

Rank and RSI for the taxa listed as rank stability island in the main document.
